New computer? Get you.
\\

Here is a quick setup guide to get you back working with Git.
\\

\section{Git software}

You might already have Git installed, to check run:

\begin{minted}{bash}
    git --version
\end{minted}

If you get something like \texttt{git version 2.23.0} then you have Git installed.
\\

If not, then head over to \href{https://git-scm.com/}{Git's website} and download the tool.

\section{Git repository host: E.g. GitHub}

There are many places you can host your Git project (known as repositories).
\\

On the Bootcamp we use GitHub.

\subsection{Sign up for an account on GitHub.com}

If you don't already have one, \href{https://github.com/join}{sign up} for an account.
\\

\subsection{Who are you?}

To avoid you needing to enter your GitHub username and password everytime Git interacts with GitHub we can setup SSH keys.
\\

To check if these are in place:

\begin{minted}{bash}
    ssh git@github.com
\end{minted}

You should get something like this with \texttt{[username]} replaced with your username:

\begin{minted}{text}
    Hi [username]! You've successfully authenticated, but GitHub does not provide shell access.
\end{minted}

\subsection{SSH access to github.com not working?}

Before you create some new SSH keys, worth checking if you already have some with:

\begin{minted}{bash}
    tail ~/.ssh/id_rsa.pub
\end{minted}

If you you get a screen of nonsense like this:

\begin{minted}{text}
    ssh-rsa AAAAB3NzaC1yc2EAAAADAQABAAACAQCiMYAAHN7k2AS2ygLhxXoFFW68Cv+eQCOEkQka
    AaPL7lgZppaoQoQ9Y/k6uky+JLd5BnXCyYV0d6APWWKxKkeE+0OodKdrPN394yBkYIQyOL0Eqsj9
    CFK06Z1qbWWY/70rLUql0W232eoS8Ct6IHX/kw0d+ePYiGaXKssVwBb8IkdFQ4FZFv+QG7aZHCLW
    e8wjt0DnQni11XDoG0Jh1Ea/V0MYCzSW71wmACd56HJmkwM4MB9RSrKUevDy14YnK/4Qr14WdDn4
    vxCueX9ulFEkmPbjDUH8XUi3vGmecDUO+38sgg+BVbbonc23zR+fR9OH6mUPR4+4u3tA/2W8RmJN
    P+8nMbVj8ttP18GIvp6FKHj6U14w5q+muJKn1Y32KWxhR1phhxACUmihwb9D4cTpcDgpC0QsLKsh
    Jn8BUomMZ3K4Vx9CDyfKv/DABr/wQpoMOGnD1gOUkiBNOQTY0e9s+/o4xO4izF+AkGWdSo+FrTEB
    dH/v+DLNAJR1gG6DtmW1vfuy95d3jpwnT8d3tkEnw2/JDhPNGX3UZQKdzLHstCjG0NlhDXf+M4rq
    dDSoV9FZ00KCmOjPO4pl4Y93g1WFd3kpyLvqLh4GWvvY3D3MSoVWNifzavSiw9g+rMSbwAh8uUTu
    pHce7Pbodn7joNetQebKWzLXEZNXaaq+a75PVQ== your_email@email.com
\end{minted}

If not (you get \texttt{No such file or directory}), then you'll need to generate a new keypair using \href{https://help.github.com/en/articles/generating-a-new-ssh-key-and-adding-it-to-the-ssh-agent}{GitHub's suggested process}:\footnote{At the \texttt{Enter passphrase (empty for no passphrase)} step I'd suggest just hitting \texttt{[Enter]} providing no password.}

\begin{minted}{bash}
    ssh-keygen -t rsa -b 4096 -C "your_email@example.com"
\end{minted}

Replace \texttt{your\_email@example.com} with your own email or comment (this is what the \texttt{-C} flag means; comment).\footnote{You often provide your email or name here as your SSH key may end up in a few places other people may find it. To prevent them removing it erroneously it helps them identify who's key it is and if it is still needed.}

Once you've finished creating your keys, output the public part\footnote{the part ending  \texttt{.pub}, the other part is the private part and should be treated like a password; never shared.} key with:

\begin{minted}{bash}
    cat ~/.ssh/id_rsa.pub
\end{minted}

Then add key to your GitHub account in \href{https://github.com/settings/ssh}{your account settings}.
\\

Finally, test your key with:

\begin{minted}{bash}
    ssh git@github.com
\end{minted}

\subsection{Other setup}

\subsubsection{Using VS Code as your default editor}

\textbf{Mac}

In VS Code: \texttt{shift + cmd + P}
\\

Type or paste \texttt{> Shell Command: Install 'Code' command in path} hit \texttt{[Enter]}
\\

\textbf{Windows}

In VS Code: \texttt{shift + ctrl + P}
\\

Type or paste `> Shell Command: Install 'Code' command in path` hit `[Enter]`
\\

Make sure you selected Add to PATH during the installation.
\\

\textbf{All systems}
\\

From the command line, run
\\

\begin{minted}{bash}
    git config --global core.editor "code --wait"
\end{minted}

\subsubsection{Setting commit author}

So that Git knows who your commits are made by:

\begin{minted}{bash}
    git config --global --edit
\end{minted}

Then edit values as required and uncomment (by removing \#).
\\

Then, to save and close the file.
\\